### 2021-11-24 sections/experience.tex
Update experience.tex

\begin{cventries}
\cventry
{Instructor Professor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2019 - on leave}
{Management and Public Policies Department, Faculty of Administration and Economics}\vspace{1.5mm}

>>>>

\begin{cventries}
\cventry
{Instructor Professor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2019 - on leave}
{Management and Public Policies Department, Faculty of Administration and Economics} \vspace{1.5mm}
